Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-02 edubots_surveys.Rnw
Turn table sideways

%%% Load packages
\usepackage{amsthm,amsmath}
\usepackage{multirow}

@@

%%% Begin ...
\begin{document}
%\SweaveOpts{concordance=TRUE}

@@

%TODO: This table is not referenced in the text
\begin{table}[h!tbp]
\begin{tabular}{lllll}
\hline
\multicolumn{1}{c}{Messaging App} & \multicolumn{2}{c}{Yes} & \multicolumn{2}{l}{No} \\ \cline{2-5} 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Frequency} & \multicolumn{1}{c}{\%} & Frequency & \multicolumn{1}{c}{\%} \\ \hline
Telegram & 62 & 22.0 & 220 & 78.0 \\
WhatsApp & 124 & 44.0 & 158 & 56.0 \\
Slack & 15 & 5.3 & 267 & 94.7 \\
Other & 60 & 21.3 & 222 & 78.7 \\
\begin{tabular}[c]{@{}l@{}}Provided by the Academic\\ Institution\end{tabular} & 159 & 56.4 & 123 & 43.6 \\
None & 19 & 6.7 & 263 & 93.3 \\ \hline
\end{tabular}
\caption{Use of messaging apps in class}
\label{tab:use_messapps}
\end{table}

\begin{table}[h!tbp]
\begin{tabular}{llccc}
\hline
 & \multicolumn{1}{c}{} & \multicolumn{2}{c}{Sector} & Total \\ \cline{3-5} 
 & \multicolumn{1}{c}{} & \begin{tabular}[c]{@{}c@{}}University \\ (f)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Vocational\\ (f)\end{tabular} &  \\ \cline{2-5} 
\multirow{4}{*}{\begin{tabular}[c]{@{}l@{}}Post-covid\\ changes\end{tabular}} & \begin{tabular}[c]{@{}l@{}}Yes, I use a safer messaging \\ app now\end{tabular} & 27 & 13 & 40 \\
 & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t use any \\ messaging app before, but \\ do use it now\end{tabular} & 31 & 13 & 44 \\
 & \begin{tabular}[c]{@{}l@{}}No, I did use it before and \\ use it now\end{tabular} & 105 & 60 & 165 \\
 & \begin{tabular}[c]{@{}l@{}}No, I didn’t use it before and \\ don’t use it now\end{tabular} & 22 & 2 & 24 \\
Total &  & 193 & 89 & 282 \\ \hline
\end{tabular}
\caption{Sector * post-covid changes crosstabulation}
\label{tab:sector*covid}
\end{table}

@@

\begin{table}[h!tbp]
\begin{tabular}{llccc}
\hline
 & \multicolumn{1}{c}{} & \multicolumn{2}{c}{FAQs} & Total \\ \cline{3-5} 
 & \multicolumn{1}{c}{} & Yes & No &  \\ \cline{2-5} 
\multirow{2}{*}{Agenda} & Yes & 103 & 68 & 171 \\
 & No & 45 & 66 & 111 \\
Total &  & 148 & 134 & 282 \\ \hline
\end{tabular}
\caption{Agenda use case * FAQs use case crosstabulation }
\label{tab:agenda*faq}
\end{table}

@@

\begin{table}[h!tbp]
\begin{tabular}{lllll}
\hline
\multicolumn{1}{c}{Kind of interactions} & \multicolumn{2}{c}{Yes} & \multicolumn{2}{l}{No} \\ \cline{2-5} 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Frequency} & \multicolumn{1}{c}{\%} & Frequency & \multicolumn{1}{c}{\%} \\ \hline
\begin{tabular}[c]{@{}l@{}}Chat interactions among \\ students in the same course\end{tabular} & 171 & 60.6 & 110 & 39.0 \\
\begin{tabular}[c]{@{}l@{}}Chat interactions among students, \\ teachers, and the faculty\end{tabular} & 13 & 4.6 & 269 & 95.4 \\
\begin{tabular}[c]{@{}l@{}}Chat interactions among students \\ of the same study year and teachers\end{tabular} & 51 & 18.1 & 231 & 81.9 \\
\begin{tabular}[c]{@{}l@{}}Teacher not being part of the \\ interaction\end{tabular} & 113 & 40.1 & 169 & 59.9 \\ \hline
\end{tabular}
\caption{Kind of interactions preferred}
\label{tab:kindinteractions}
\end{table}

@@

Analytics & 108 & 52.7 & 97 & 47.3 \\
Connectivity & 119 & 58.0 & 86 & 42.0 \\
Familiarity & 121 & 59.0 & 84 & 41.0 \\
Hidden Phone & 113 & 55.1 & 92 & 44.9 \\
Horizontally & 134 & 65.4 & 71 & 34.6 \\
Official formation & 42 & 20.5 & 163 & 79.5 \\
Pluggability & 65 & 31.7 & 140 & 68.3 \\
Sustainability & 157 & 76.6 & 48 & 23.4\\
Unidirectionality & 27 & 13.2 & 178 & 86.8 \\
Officiality & 150 & 73.2 & 55 & 26.8 \\
Synchrony & 45 & 22.0 & 160 & 78.0\\
Other & 5 & 2.4 & 200 & 97.6 \\
\hline
\end{tabular}\caption{Interaction media features valued by teachers}
\label{tab:interaction}
\end{table}

@@

%TODO - table fits better in landscape? try to fit in page size 
\begin{table}[h!tbp]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{llllllllllll}
\hline
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Analytics} & Connectivity & Familiarity & Hidden phone & Horizontallity & \begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} & Pluggability & Sustainability & Unidirectionality & Officiality & Synchrony \\ \hline
Analytics & \multicolumn{1}{c}{-} & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 12.172^{***}$} & $X^{2}_{(1, N = 205)} = 4.855^{*}$ & ns & ns & $X^{2}_{(1, N = 205)} = 4.144^{*}$ & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 12.490^{***}$} & $X^{2}_{(1, N = 205)} = 4.314^{*}$ & ns & ns & ns \\
Connectivity & \multicolumn{1}{c}{} & \multicolumn{1}{c}{-} & ns & ns & $X^{2}_{(1, N = 205)} = 5.971^{***}$ & ns & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 16.286^{***}$} & ns & ns & ns & ns \\
Familiarity &  &  & - & ns & ns & ns & ns & ns & ns & ns & ns \\
Hidden phone &  &  &  & - & ns & $X^{2}_{(1, N = 205)} = 5.678^{*}$ & $X^{2}_{(1, N = 205)} = 4.683^{*}$ & ns & $X^{2}_{(1, N = 205)} = 4.515^{*}$ & ns & ns \\
Horizontallity &  &  &  &  & - & ns & ns & ns & ns & $X^{2}_{(1, N = 205)} = 5.453^{*}$ & ns \\
\begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} &  &  &  &  &  & - & $X^{2}_{(1, N = 205)} = 8.163^{**}$ & ns & ns & ns & ns \\
Pluggability &  &  &  &  &  &  & - & ns & ns & ns & ns \\
Sustainability &  &  &  &  &  &  &  & - & ns & ns & ns \\
Unidirectionality &  &  &  &  &  &  &  &  & - & ns & ns \\
Officiality &  &  &  &  &  &  &  &  &  & - & ns \\
Synchrony & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  &  &  & \multicolumn{1}{c}{} &  &  &  & - \\ \hline
\end{tabular}}
\caption{Interaction media features analysis ($^{***}p<0.001$, $^{**}p<0.01$, $^{*}p<0.05$).}
\label{tab:interactionfeatures}
\end{table}

>>>>

%%% Load packages
\usepackage{amsthm,amsmath}
\usepackage{multirow}
\usepackage{rotating}

@@

%%% Begin ...
\begin{document}

@@

%TODO: This table is not referenced in the text
\begin{table}[h!tbp]
\begin{tabular}{lllll}
\hline
\multicolumn{1}{c}{Messaging App} & \multicolumn{2}{c}{Yes} & \multicolumn{2}{l}{No} \\ \cline{2-5} 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Frequency} & \multicolumn{1}{c}{\%} & Frequency & \multicolumn{1}{c}{\%} \\ \hline
Telegram & 62 & 22.0 & 220 & 78.0 \\
WhatsApp & 124 & 44.0 & 158 & 56.0 \\
Slack & 15 & 5.3 & 267 & 94.7 \\
Other & 60 & 21.3 & 222 & 78.7 \\
\begin{tabular}[c]{@{}l@{}}Provided by the Academic\\ Institution\end{tabular} & 159 & 56.4 & 123 & 43.6 \\
None & 19 & 6.7 & 263 & 93.3 \\ \hline
\end{tabular}
\vspace{0.8em}
\caption{Use of messaging apps in class}
\label{tab:use_messapps}
\end{table}

\begin{table}[h!tbp]
\begin{tabular}{llccc}
\hline
 & \multicolumn{1}{c}{} & \multicolumn{2}{c}{Sector} & Total \\ \cline{3-5} 
 & \multicolumn{1}{c}{} & \begin{tabular}[c]{@{}c@{}}University \\ (f)\end{tabular} & \begin{tabular}[c]{@{}c@{}}Vocational\\ (f)\end{tabular} &  \\ \cline{2-5} 
\multirow{4}{*}{\begin{tabular}[c]{@{}l@{}}Post-covid\\ changes\end{tabular}} & \begin{tabular}[c]{@{}l@{}}Yes, I use a safer messaging \\ app now\end{tabular} & 27 & 13 & 40 \\
 & \begin{tabular}[c]{@{}l@{}}Yes, I didn’t use any \\ messaging app before, but \\ do use it now\end{tabular} & 31 & 13 & 44 \\
 & \begin{tabular}[c]{@{}l@{}}No, I did use it before and \\ use it now\end{tabular} & 105 & 60 & 165 \\
 & \begin{tabular}[c]{@{}l@{}}No, I didn’t use it before and \\ don’t use it now\end{tabular} & 22 & 2 & 24 \\
Total &  & 193 & 89 & 282 \\ \hline
\end{tabular}
\vspace{0.8em}
\caption{Sector * post-covid changes crosstabulation}
\label{tab:sector*covid}
\end{table}

@@

\begin{table}[h!tbp]
\begin{tabular}{llccc}
\hline
 & \multicolumn{1}{c}{} & \multicolumn{2}{c}{FAQs} & Total \\ \cline{3-5} 
 & \multicolumn{1}{c}{} & Yes & No &  \\ \cline{2-5} 
\multirow{2}{*}{Agenda} & Yes & 103 & 68 & 171 \\
 & No & 45 & 66 & 111 \\
Total &  & 148 & 134 & 282 \\ \hline
\end{tabular}
\vspace{0.8em}
\caption{Agenda use case * FAQs use case crosstabulation }
\label{tab:agenda*faq}
\end{table}

@@

\begin{table}[h!tbp]
\begin{tabular}{lllll}
\hline
\multicolumn{1}{c}{Kind of interactions} & \multicolumn{2}{c}{Yes} & \multicolumn{2}{l}{No} \\ \cline{2-5} 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Frequency} & \multicolumn{1}{c}{\%} & Frequency & \multicolumn{1}{c}{\%} \\ \hline
\begin{tabular}[c]{@{}l@{}}Chat interactions among \\ students in the same course\end{tabular} & 171 & 60.6 & 110 & 39.0 \\
\begin{tabular}[c]{@{}l@{}}Chat interactions among students, \\ teachers, and the faculty\end{tabular} & 13 & 4.6 & 269 & 95.4 \\
\begin{tabular}[c]{@{}l@{}}Chat interactions among students \\ of the same study year and teachers\end{tabular} & 51 & 18.1 & 231 & 81.9 \\
\begin{tabular}[c]{@{}l@{}}Teacher not being part of the \\ interaction\end{tabular} & 113 & 40.1 & 169 & 59.9 \\ \hline
\end{tabular}
\vspace{0.8em}
\caption{Kind of interactions preferred}
\label{tab:kindinteractions}
\end{table}

@@

Analytics & 108 & 52.7 & 97 & 47.3 \\
Connectivity & 119 & 58.0 & 86 & 42.0 \\
Familiarity & 121 & 59.0 & 84 & 41.0 \\
Hidden Phone Number & 113 & 55.1 & 92 & 44.9 \\
Horizontally & 134 & 65.4 & 71 & 34.6 \\
Official formation & 42 & 20.5 & 163 & 79.5 \\
Pluggability & 65 & 31.7 & 140 & 68.3 \\
Sustainability & 157 & 76.6 & 48 & 23.4\\
Unidirectionality & 27 & 13.2 & 178 & 86.8 \\
Officiality & 150 & 73.2 & 55 & 26.8 \\
Synchrony & 45 & 22.0 & 160 & 78.0\\
Other & 5 & 2.4 & 200 & 97.6 \\
\hline
\end{tabular}
\vspace{0.8em}
\caption{Interaction media features valued by teachers}
\label{tab:interaction}
\end{table}

@@

%TODO - table fits better in landscape? try to fit in page size 
\begin{sidewaystable}[h!tbp]
\centering
\resizebox{\textwidth}{!}{\begin{tabular}{llllllllllll}
\hline
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Analytics} & Connectivity & Familiarity & Hidden phone & Horizontallity & \begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} & Pluggability & Sustainability & Unidirectionality & Officiality & Synchrony \\ \hline
Analytics & \multicolumn{1}{c}{-} & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 12.172^{***}$} & $X^{2}_{(1, N = 205)} = 4.855^{*}$ & ns & ns & $X^{2}_{(1, N = 205)} = 4.144^{*}$ & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 12.490^{***}$} & $X^{2}_{(1, N = 205)} = 4.314^{*}$ & ns & ns & ns \\
Connectivity & \multicolumn{1}{c}{} & \multicolumn{1}{c}{-} & ns & ns & $X^{2}_{(1, N = 205)} = 5.971^{***}$ & ns & \multicolumn{1}{c}{$X^{2}_{(1, N = 205)} = 16.286^{***}$} & ns & ns & ns & ns \\
Familiarity &  &  & - & ns & ns & ns & ns & ns & ns & ns & ns \\
Hidden phone &  &  &  & - & ns & $X^{2}_{(1, N = 205)} = 5.678^{*}$ & $X^{2}_{(1, N = 205)} = 4.683^{*}$ & ns & $X^{2}_{(1, N = 205)} = 4.515^{*}$ & ns & ns \\
Horizontallity &  &  &  &  & - & ns & ns & ns & ns & $X^{2}_{(1, N = 205)} = 5.453^{*}$ & ns \\
\begin{tabular}[c]{@{}l@{}}Official\\  formation\end{tabular} &  &  &  &  &  & - & $X^{2}_{(1, N = 205)} = 8.163^{**}$ & ns & ns & ns & ns \\
Pluggability &  &  &  &  &  &  & - & ns & ns & ns & ns \\
Sustainability &  &  &  &  &  &  &  & - & ns & ns & ns \\
Unidirectionality &  &  &  &  &  &  &  &  & - & ns & ns \\
Officiality &  &  &  &  &  &  &  &  &  & - & ns \\
Synchrony & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &  &  &  &  & \multicolumn{1}{c}{} &  &  &  & - \\ \hline
\end{tabular}}
\caption{Interaction media features analysis ($^{***}p<0.001$, $^{**}p<0.01$, $^{*}p<0.05$).}
\label{tab:interactionfeatures}
\end{sidewaystable}
